Couple selection in UKBB

### 2021-09-14 analysis/couple_selection.Rmd
update some docs

Each phenotype in the SGG database was filtered for the following criteria based on the genetic qc file (found here `r files_ref %>% filter(custom_names == "sqc") %>% pull(files)`:

@@

Within the European, genetic, consenting sample, we limited to only individuals which came from households with exactly two participants in the UKBB based on the file: `r files_ref %>% filter(custom_names == "household_info") %>% pull(files)`

@@

Household couples defined above were filtered based on kinship (estimate of the kinship coefficient for pair based on the set of markers used in the kinship inference) from the following file: `r tar_read(path_relatives)`. Couples were excluded if kinship was > `0.05`.

@@

Finally, using the data at data-field `6141`, ["How are people in household related to participant"](https://biobank.ctsu.ox.ac.uk/showcase/field.cgi?id=6141), heterosexual, unrelated, household pairs were filtered to only include couples who both said: `Husband, wife, or partner`.

```{r hh_pairs_filtering3,  include = FALSE}

>>>>

Each phenotype in the SGG database was filtered for the following criteria based on the genetic qc file (located here: ``r files_ref %>% filter(custom_names == "sqc") %>% pull(files)``):

@@

Within the European, genetic, consenting sample, we limited to only individuals which came from households with exactly two participants in the UKBB based on the file: ``r files_ref %>% filter(custom_names == "household_info") %>% pull(files)``.

@@

Household couples defined above were filtered based on kinship (estimate of the kinship coefficient for pair based on the set of markers used in the kinship inference) from the following file: ``r files_ref %>% filter(custom_names == "relatives") %>% pull(files)``. Couples were excluded if kinship was > `0.05`.

@@

Finally, using the data at data-field `6141`, ["How are people in household related to participant"](https://biobank.ctsu.ox.ac.uk/showcase/field.cgi?id=6141), the heterosexual, unrelated, household pairs were filtered to only include couples who both responded `Husband, wife, or partner`.

```{r hh_pairs_filtering4,  include = FALSE}
